---
title: "Introduction to random walks"
author:
  - Randomwalk Enthusiast:
      email: random@walk.edu
      institute: [UofRW]
      correspondence: true
institute:
  - UofRW: University of Random Walks
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Random walks - aren't they great? Useful for everything from modeling animal movement behavior to predicting stock markets. Well, at least for providing a null model.
keywords: |
  random; walks
---

Keywords: `r rmarkdown::metadata$keywords`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
library(simplerc)
```

# Introduction

The random walk is a useful statistical tool. Here we show how to simulate, plot, and fit random walks.

# Methods

## Simulation

We simulate a Gaussian random walk by taking the cumulative sum of random normal numbers.

## Visualization

Random walks are best visualized as a line plot.

## Fitting

Given a sequence of positions, the step lengths of the sequence is the difference between positions. The parameters of the Gaussian random walk ($\mu$ and $\sigma$) are the mean and standard deviation of the step lengths, respectively.

# Results

Figure \@ref(fig:fig1) shows a simulated random walk with $\mu$ = 0.1 and $\sigma$ = 2 over 100 time steps.

```{r fig1, fig.cap="A random walk"}
t <- 100
mu <- 0.5
sigma <- 2

walk <- simulate_walk(t, mu, sigma)
plot_walk(walk)
```

```{r fit}
params <- fit_walk(walk)
```

The fitted walk estimated parameters of $\mu$ = `r params$mu` and $\sigma$ = `r params$sigma`.

# Conclusion

Gee aren't random walks swell.

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
